\newpage
\vspace{-1cm}
\chapter*{\zihao{-2}\heiti{ABSTRACT}}
\vspace{-0.5cm}

%With the rapid development of cities and the growing number of urban car ownership, intelligent transportation has become an important research field in academia and industry. However, traffic congestion leads to the reduction of emergency resource allocation efficiency of the transportation network, and the problem of emergency vehicles(EVs) being blocked on the road is becoming more and more prominent. Fast passage of EVs has become a research hotspot of intelligent transportation, and its research results can promote the shortening of rescue time of EVs, which is crucial to save lives and reduce property damage. Traditionally, most of the methods to achieve fast passage of EVs are to provide green light signals for EVs at intersections, so that EVs can pass through intersections without stopping. The EV is affected by other vehicles in the roadway, which limits the high speed of the EV and leads to longer travel time. This paper focuses on the impact of other vehicles on the road on EVs, studies the relationship between EVs, other vehicles on the road, and traffic signals, and designs a traffic signal intelligent con6figuration method for EVs to pass quickly, providing a "green belt" for EVs to travel at high speed. This paper mainly researches the following three aspects.

%First of all, build the fastest path model for emergency vehicles, distributed agent models at intersections, and traffic light control models. Under the control of the intelligent body, the traffic signal transitions in the unsolicited phase, the reduced road saturation phase, the signal preemption phase, and the restored traffic flow phase.

Smart transportation is an important research area of smart cities, and the signal control method for emergency vehicles (EV) is a research hotspot of smart transportation, and its research results can promote shortening the rescue time of EVs, which is crucial to save lives and reduce property damage. Traditionally, most of the methods to achieve fast passage of EVs are to provide green light signals for EVs using sensors or manual control, so that EVs can cross the intersection smoothly without stopping. With the increase of car ownership, distributed traffic signal control methods have become an emerging technology for smart transportation. In this paper, we propose an intelligent traffic signal control method for EVs to pass through the traffic light intersection without stopping, and provide a "green belt" for EVs to drive smoothly at high speed. In this paper, three main aspects are studied.

%Firstly, we construct an intelligent traffic signal control system architecture for EV priority passage. On this basis, we construct the fastest path "green belt" model and the corresponding distributed intelligent body model, and design the traffic signal intelligent control algorithm, so that the traffic signal transitions in the no-request stage, saturation-reduction stage, signal-preemption stage and restoration stage.

Firstly, we construct the fastest path "green belt" model. On this basis, we construct the corresponding distributed intelligent agent model and the intelligent traffic signal control system architecture for EV priority passage.  We design the traffic signal intelligent control algorithm, so that the traffic signal transitions in the no-request stage, saturation-reduction stage, signal-preemption stage and restoration stage.

Next, the intelligent traffic signal configuration method is designed for EV priority. The first step reduces the road saturation on the path of EVs by adjusting the traffic signal green time, so that other vehicles in front of the EV have space to give way to the EV, thus enabling the EV to drive at high speed. The second step is to provide the green signal for EVs through a combination of non-intrusive preemption and intrusive preemption so that EVs can quickly pass through the traffic light intersection in the green light duration. The third step restores the traffic flow in all directions at the intersection through a linear planning method to reduce the disturbance caused by EVs' priority traffic to the whole traffic. In the second and third steps, this paper considers the intersections passed by the EV in real-time and predicts the number of queued vehicles.


Finally, we conduct a series of experiments on the feasibility and advancement of an intelligent control method of traffic signals for EV priority passage in the traffic simulator SUMO. The results show that, compared with the fixed-time control method (FTCM), Min's flexible signal preemption method (FSPM), and Qin's EV signal pre-emption method (EVSP), our method can optimize travel time by up to 62.85\%, 50.83\%, and 11.62\%, respectively. In addition, the experimental results show that this method does not cause a significant impact on the traffic network.


%compared with the fixed-time control method (FTCM), this method can effectively reduce the travel time of EVs by 62.85\%; compared with the flexible signal preemption method (FSPM), this method can effectively reduce the travel time of EVs by 50.85\%; compared with the EV signal pre-emption method (EVSP), this method can effectively reduce the travel time of EVs by 11.62\%. In addition, the experimental results show that this method does not cause a significant impact on the traffic network.


%In this paper, we conduct a series of experiments on the feasibility and advancement of an intelligent control method of traffic signals for EV priority passage in the traffic simulator SUMO.

%{\sihao{\textbf{Keywords:}}} \textit{Intelligent Transportation Systems, Traffic Signal Control, Emergency Vehicles, Signal Preemption, Signal Timing, Queueing Analysis}

{\sihao{\textbf{Keywords:}}} \textit{Intelligent Transportation Systems, Traffic Signal Control, Emergency Vehicles, Signal Preemption, Signal Timing}